---
title: "Some analysis of the POLLnet data"
author: "Giovanni Bonafè"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Some analysis of the POLLnet data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First we extract some data.
```{r  error=FALSE, message=FALSE, warning=FALSE, fig.width=7}
library(pollnet)
dat <- pollnet_data_station(part_id = 1373,
                            stat_id = 84,
                            from = "2011-01-01",
                            to   = "2018-12-31")
```

Pollen concentrations can be classified according to the limits provided by function `pollnet_particles`.
```{r message=FALSE, warning=FALSE}
pp <- pollnet_particles()
breaks <- c(0, pp[pp$PART_ID==1373, c("PART_LOW", "PART_MIDDLE", "PART_HIGH")], Inf)
library(lubridate)
library(dplyr)
library(tidyr)
library(knitr)
dat %>%
  filter(!is.na(REMA_CONCENTRATION)) %>%
  mutate(Month = lubridate::month(REMA_DATE),
         Conc = cut(REMA_CONCENTRATION, 
                    breaks=breaks, 
                    include.lowest = T)) %>%
  group_by(Month, Conc) %>%
  summarize(Ndays=n()) %>%
  spread(key = Conc, value = Ndays, fill = 0) %>%
  kable(row.names = F)
```

Another R package, `pollen`, provides tools for working with aerobiological data. Have a look [here](https://nowosad.github.io/pollen/) and [here](https://cdn.rawgit.com/Nowosad/pollen/master/vignettes/intro.html). With the function `pollen_season` we can calculate pollen season limits.
```{r}
library(pollen)
df <- dat %>% 
  filter(!is.na(REMA_CONCENTRATION)) %>%
  mutate(DATE=as.Date(REMA_DATE))
pollen_season(value = df$REMA_CONCENTRATION, date  = df$DATE, method = "95")
```

Different methods can lead to different estimations
```{r error=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=2}
library(purrr)
ps_methods <- c("90", "95", "98", "Jager", "Lejoly")
names(ps_methods) <- ps_methods
df_seasons <- ps_methods %>%
  map_dfr(~pollen_season(method = ., 
                         value  = df$REMA_CONCENTRATION, 
                         date   = df$DATE),
          .id = "method")
library(ggplot2)
ggplot(df_seasons) + 
  geom_crossbar(fatten=0,
                aes(x=method, y=start, 
                    ymin=start, ymax=end, 
                    group=paste(method,year,start)),
                col="orange")+
  geom_text(aes(x=method, y=start, 
                label=paste0(format(start,"%d/%m"),"-\n",format(end,"%d/%m/%Y"))), 
            size=2.5, adj=0)+
  coord_flip()+
  theme_minimal()+
  theme(axis.title.x =element_blank(),
        axis.text.x  =element_blank(),
        axis.ticks.x =element_blank())
```



```{r error=FALSE, message=FALSE, warning=FALSE, fig.height=12, fig.width=6}
## FORSE PRIMA MEGLIO TOGLIERE OUTLIERS CON outliers_replacer
dat <- pollnet_data(part_ids = c(1373,1378,1391), 
                    from = "2018-04-01", 
                    to   = "2018-04-10")
breaks <- c(0,quantile(dat$REMA_CONCENTRATION[dat$REMA_CONCENTRATION>0],
                   c(0.0001,0.001,0.01,0.7), na.rm=T))
ggplot(dat, aes(x = LONGITUDE, y = LATITUDE,
                colour = REMA_CONCENTRATION)) +
  geom_point(alpha = 0.7) +
#  scale_colour_gradientn(colours = c("grey80","olivedrab","orange","red","purple"),
#                         values = breaks) +
  facet_grid(REMA_DATE~PART_NAME_L)+
  theme_bw()
```





