---
title: "Extract data from the POLLnet database"
author: "Giovanni Bonafè"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extract data from the POLLnet database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The R package `pollnet` gives access to pollen and spores data collected by the Italian monitoring network. More information about the network [here](http://dati.retecivica.bz.it/it/dataset/italian-pollnet-webservices).

In an R session, you can install the package as follows
```{r eval = FALSE}
devtools::install_github("jobonaf/pollnet")
```

Once installed and loaded, let's see a list of the available functions
```{r}
library(pollnet)
lsf.str("package:pollnet")
```

We can get a list of the available particles with function `pollnet_particles`:
```{r}
pp <- pollnet_particles ()
knitr::kable(pp[,c("PART_ID", "PART_NAME_L")])
```

Italian regions are identified with numeric codes
```{r}
pr <- pollnet_regions ()
knitr::kable(pr)
```

With function `pollnet_stations` we can get metadata of the stations, specifying a single region
```{r}
ps <- pollnet_stations (regi_id = 27)
knitr::kable(ps)
```

We can extract metadata of all the Italian stations as well. Packages `leaflet` and `htmltools` help us plotting them in an interactive map.
```{r}
ps <- pollnet_stations ()
library(leaflet)
library(htmltools)
leaflet(ps, width = 600, height = 400) %>% 
  addTiles() %>%
  addCircleMarkers(label = ~htmlEscape(STAT_NAME_I), radius = 5)
```

Now we can extract measured data. For example of birch pollen (_Betula_, __1373__). Package `dplyr` help us summarizing the results: we can display the highest data for each region.
```{r error=FALSE, message=FALSE, warning=FALSE}
dat <- pollnet_data(part_ids = 1373, 
                    from = "2019-03-01", 
                    to = "2019-03-07")
library(dplyr)
dat %>% 
  group_by(REGI_NAME_I) %>% 
  arrange(desc(REMA_CONCENTRATION)) %>% 
  slice(1) %>% 
  select(REMA_DATE, REMA_CONCENTRATION, REGI_NAME_I, STAT_NAME_I) %>%
  knitr::kable()
```

Extracting a single station and a single pollen type is faster. Package `ggplot2` help us plotting the data.
```{r  error=FALSE, message=FALSE, warning=FALSE, fig.width=7}
dat <- pollnet_data_station(part_id = 1373,
                            stat_id = 84,
                            from = "2011-01-01",
                            to   = "2018-12-31")
library(ggplot2)
ggplot(dat) +
  geom_line(aes(x=REMA_DATE, 
                y=REMA_CONCENTRATION, 
                col=STAT_NAME_I))
```






